% BluesScaleRiffs without exercises
% Same as Lesson2 but without exercises
    \subsection{Blues Scale Riffs}
        \begin{itemize}
            \item Each riff we learn is based on the Blues Scale (we're learning the scale as we learn the riffs).
            \item We can use these riffs in solos
            % \item Remember: 3 blow is the same as 2 draw, but we prefer 2 draw
        \end{itemize}

\part{Learning the Blues Scale One Section at a time}
    \section{Blues Riffs on The Blues Scale}
    The top end of the blues scale is easy. 
    \\ We will go up the scale, then down the scale. \Uparrow \Downarrow
        \section*{Top End - Blues Scale}
            \subsection*{Blues Scale - Top End \Uparrow}
                \4\5\6\\
                
            \subsection*{Blues Scale - Top End \Downarrow}
                \6\5\4 
                
\newpage    
        \section*{Bottom End - Blues Scale}
        The BOTTOM end of the blues scale is harder. We will learn 3 levels - Easy, Moderate, Hard.
            \subsection*{Easy - Bottom End}
            In the easy version, a couple of the notes from the blues scale are missing.
                
                \subsection*{Blues Scale - Bottom End \Downarrow Level: Easy}
                % {\textit{Level: Easy}}\\
                    \4\3\2 \\
                
                \subsection*{Blues Scale - Bottom End \Uparrow Level: Easy}
                    \2 \3 \4
        
        \newpage
            \subsection*{Moderate}
            In the moderate version, there is 1 note missing from the blues scale.

                \subsection*{Blues Scale - Bottom End \Downarrow Level: Moderate}
                    \4\four\3\2 \\
                
                \subsection*{Blues Scale - Bottom End \Uparrow Level: Moderate}
                    \2\3\four\4
        
        
        \newpage    
            \subsection*{Hard}
            In the moderate version, there are no notes missing from the blues scale.
            This version includes the 4 draw bend - (\textit{Also known as the 'Tritone' or the 'Devils Interval'}).
                \subsection*{Blues Scale - Bottom End \Downarrow Level: Hard}
                    \4\e\four\3\2 \\
                
                \subsection*{Blues Scale - Bottom End \Uparrow Level: Hard}
                    \2\3\four\e\4
            